Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-08-24 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd

[Response:] Thanks for pointing these out. We have updated the introduction as well as the discussion parts in order to better showing that these participants actually represent those in the lower range of milk intake. Discussion comparing our findings with previous studies conducted in East Asian population has been expanded in more details. The fact that reference 19 was looking into CVD and all-cause mortality has been clarified.

2. *I am unfortunately not familiar with the Bayesian models used in this work. I am sure that many readers will be in a similar situation as me. I appreciate that these models can calculate hazard ratios without fulfilling the proportional hazards assumption. The authors should in more detail describe the benefits and limitations of these models in relation to the more commonly used Cox proportional hazards regression. Is a HR estimated from these models directly comparable with that from a Cox model? How is an acceleration factor interpreted? Do the models assume that a higher milk intake is associated with a lower stroke mortality, indicated also by the Pr(HR<1)? If so, how would that influence the validity of the method since you in the introduction write that there are reports of inverse associations, no association, and direct associations? In Table 2, both SD and 95% CrI are given. Is there a reason for specifying the SD?*

2. *Why were analyses performed stratified by sex? Since no pooled analysis is presented, the reason for a stratified analysis should be stated in the aims, unless this was a secondary analysis and then also the results from the total cohort should be presented. The authors should also discuss the observed sex differences in more detail. Do other studies show similar sex differences? What potential biological mechanisms may explain them?*

[Response:] It is reasonable to conduct the analysis separated in men and women since we expected there is a sex difference in the association based on our prior information from the same cohort as well as the Singapore Chinese Health Study. Our expectation was further confirmed through a quick likelihood ratio test comparing Cox proportional hazard models with and without the interaction terms between sex and milk intake frequencies (P for interaction < 0.0001, but not shown in the main text). Our stratified analyses also suggested the AFs and HRs might be in slightly different directions among 2 out of 4 frequencies (Table 2 and Table 3, results in the "total stroke" parts), we therefore believe it is legitimate to conduct analyses stratified by sex.

The interaction effect by sex was found probably due to the fact that women in our cohort had relatively less mortality rates of fatal stroke and much better lifestyles (much less smokers and alcohol drinkers) than men, or maybe due to other factors that was not available in/considered by our models such as intake of calcium supplements. The existing beneficial effect by milk intake is probably less evident in women than that in men in the JACC study cohort.

The updated manuscript have included these information in the methods section as well as in the discussion about sex differences on the association.

### 2020-08-24 Paperfolder/Paperfolder.Rmd
Updated gender diff

Our aim was to provide a more straightforward answer to the primary research question that whether someone answered he/she drank milk at the baseline of study had lower hazard of dying from stroke compared with his/her counterparts who said they never consumed milk. If the answer to the primary objective was yes, then the probabilities that individuals with different frequencies of milk intake may had lower hazard compared with those who never drank milk were calculated through a Markov Chain Monte Carlo (MCMC) simulation process. A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay a stroke mortality event from happening after controlling for the other potential confounders. Analyses would be conducted stratified by sex or any other factor that might suggest any modification effect on the association.

@@

Since there is significant effect modification by sex found in the total sample, all of the subsequent analyses were performed in men and women separately. We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake. Age-adjusted stroke mortality rate were expressed as per 1000 person-year predicted through poisson regression models.

@@

<!-- - comparison with previous meta-analyses/studies in japan -->
These findings showed similar negative effect estimates reported previously [@wang_milk_2015] using data from the same cohort, in which the outcomes of interests were focused on cardiovascular diseases and all-cause mortality. Moreover, we have further updated the results with more comprehensive and straightforward evidence about whether and how certain the data had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men. A recent dose-response meta-analysis of 18 prospective cohort studies had shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke. The same meta-analysis also reported a greater reduction of risk of stroke (18%) for East Asian population in contrast with the 7% less risk in the pooled overall finding for all populations combined. Benefits of increased milk intake might be particularly noticeable in East Asian countries where strokes are relatively more common, and milk consumption is much lower than those studies conducted among European or American populations [@dehghan2018association]. However, the Life Span Study [@sauvaget2003intake], which was conducted about 10 years earlier than the JACC Study, reported null association between milk intake and fatal stroke among men and women combined who survived from the Hiroshima and Nagasaki atomic bomb. The difference could be largely explained by the different targeting populations between the two studies.  @kondo2013consumption also reported null association in either men or women from the NIPPON DATA80 study. In fact, the exact number of stroke mortality events was about 85% less and the number of participants in the NIPPON DATA80 was about 90% less than those in the JACC study database, their null association might likely due to its limited statistical power. @umesawa2008dietary reported that dairy calcium intake was inversely associated with ischemic stroke mortality risk which could be considered as one of the potential evidence that supported our findings. Furthermore, stronger inverse association between milk consumption and stroke mortality in men rather than in women was found in the Singapore Chinese Health Study [@Talaei_2016] as well. The reasons for this gender differences is currently unknown. It might be contributed by generally better/healthier lifestyles (much less smokers and alcohol drinkers) in women regardless of milk intake frequency, or maybe due to other factors that was not available/considered by our models such as intake of calcium supplements. The probably existing beneficial effect by milk intake is probably less evident in women than that in men. Further investigation is needed.

>>>>

Our aim was to provide a more straightforward answer to the primary research question that whether someone answered he/she drank milk at the baseline of study had lower hazard of dying from stroke compared with his/her counterparts who said they never consumed milk. If the answer to the primary objective was yes, then the probabilities that individuals with different frequencies of milk intake may had lower hazard compared with those who never drank milk were calculated through a Markov Chain Monte Carlo (MCMC) simulation process. A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay a stroke mortality event from happening after controlling for the other potential confounders.

@@

Analyses were stratified by sex as difference in milk consumption levels and mortality rate was suggested previously [@wang_milk_2015;@Talaei_2016]. We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake. Age-adjusted stroke mortality rate were expressed as per 1000 person-year predicted through poisson regression models.

@@

<!-- - comparison with previous meta-analyses/studies in japan -->
These findings showed similar negative effect estimates reported previously [@wang_milk_2015] using data from the same cohort, in which the outcomes of interests were focused on cardiovascular diseases and all-cause mortality. Moreover, we have further updated the results with more comprehensive and straightforward evidence about whether and how certain the data had shown about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event among Japanese men. A recent dose-response meta-analysis of 18 prospective cohort studies had shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke. The same meta-analysis also reported a greater reduction of risk of stroke (18%) for East Asian population in contrast with the 7% less risk in the pooled overall finding for all populations combined. Benefits of increased milk intake might be particularly noticeable in East Asian countries where strokes are relatively more common, and milk consumption is much lower than those studies conducted among European or American populations [@dehghan2018association]. However, the Life Span Study [@sauvaget2003intake], which was conducted about 10 years earlier than the JACC Study, reported null association between milk intake and fatal stroke among men and women combined who survived from the Hiroshima and Nagasaki atomic bomb. The difference could be largely explained by the different targeting populations between the two studies.  @kondo2013consumption also reported null association in either men or women from the NIPPON DATA80 study. In fact, the exact number of stroke mortality events was about 85% less and the number of participants in the NIPPON DATA80 was about 90% less than those in the JACC study database, their null association might likely due to its limited statistical power. @umesawa2008dietary reported that dairy calcium intake was inversely associated with ischemic stroke mortality risk which could be considered as one of the potential evidence that supported our findings. Furthermore, stronger inverse association between milk consumption and stroke mortality in men rather than in women was found in the Singapore Chinese Health Study [@Talaei_2016] as well. The reasons for this gender differences is currently unknown. It might be contributed by generally better/healthier lifestyles (much less smokers and alcohol drinkers) in women regardless of milk intake frequency, or maybe due to other factors that was not available in/considered by our models such as intake of calcium supplements. The probably existing beneficial effect by milk intake is probably less evident in women than that in men. Further investigation is needed.

### 2020-08-24 Paperfolder/Paperfolder.tex
Updated gender diff

Since there is significant effect modification by sex found in the total
sample, all of the subsequent analyses were performed in men and women
separately. We calculated sex-specific means (standard deviation, sd)
and proportion of selected baseline characteristics according to the
frequency of milk intake. Age-adjusted stroke mortality rate were
expressed as per 1000 person-year predicted through poisson regression
models.

@@

These findings showed similar negative effect estimates reported
previously \citep{wang_milk_2015} using data from the same cohort, in
which the outcomes of interests were focused on cardiovascular diseases
and all-cause mortality. Moreover, we have further updated the results
with more comprehensive and straightforward evidence about whether and
how certain the data had shown about daily consumption of milk is
contributing to a postponed stroke (mostly cerebral infarction)
mortality event among Japanese men. A recent dose-response meta-analysis
of 18 prospective cohort studies had shown a similar negative
association \citep{DeGoede2016} between milk consumption and risk of
stroke. The same meta-analysis also reported a greater reduction of risk
of stroke (18\%) for East Asian population in contrast with the 7\% less
risk in the pooled overall finding for all populations combined.
Benefits of increased milk intake might be particularly noticeable in
East Asian countries where strokes are relatively more common, and milk
consumption is much lower than those studies conducted among European or
American populations \citep{dehghan2018association}. However, the Life
Span Study \citep{sauvaget2003intake}, which was conducted about 10
years earlier than the JACC Study, reported null association between
milk intake and fatal stroke among men and women combined who survived
from the Hiroshima and Nagasaki atomic bomb. The difference could be
largely explained by the different targeting populations between the two
studies. \citet{kondo2013consumption} also reported null association in
either men or women from the NIPPON DATA80 study. In fact, the exact
number of stroke mortality events was about 85\% less and the number of
participants in the NIPPON DATA80 was about 90\% less than those in the
JACC study database, their null association might likely due to its
limited statistical power. \citet{umesawa2008dietary} reported that
dairy calcium intake was inversely associated with ischemic stroke
mortality risk which could be considered as one of the potential
evidence that supported our findings. Furthermore, stronger inverse
association between milk consumption and stroke mortality in men rather
than in women was found in the Singapore Chinese Health Study
\citep{Talaei_2016} as well. The reasons for this gender differences is
currently unknown. It might be contributed by generally better/healthier
lifestyles (much less smokers and alcohol drinkers) in women regardless
of milk intake frequency, or maybe due to other factors that was not
available/considered by our models such as intake of calcium
supplements. The probably existing beneficial effect by milk intake is
probably less evident in women than that in men. Further investigation
is needed.

>>>>

Analyses were stratified by sex as difference in milk consumption levels
and mortality rate was suggested previously
\citep{wang_milk_2015, Talaei_2016}. We calculated sex-specific means
(standard deviation, sd) and proportion of selected baseline
characteristics according to the frequency of milk intake. Age-adjusted
stroke mortality rate were expressed as per 1000 person-year predicted
through poisson regression models.

@@

These findings showed similar negative effect estimates reported
previously \citep{wang_milk_2015} using data from the same cohort, in
which the outcomes of interests were focused on cardiovascular diseases
and all-cause mortality. Moreover, we have further updated the results
with more comprehensive and straightforward evidence about whether and
how certain the data had shown about daily consumption of milk is
contributing to a postponed stroke (mostly cerebral infarction)
mortality event among Japanese men. A recent dose-response meta-analysis
of 18 prospective cohort studies had shown a similar negative
association \citep{DeGoede2016} between milk consumption and risk of
stroke. The same meta-analysis also reported a greater reduction of risk
of stroke (18\%) for East Asian population in contrast with the 7\% less
risk in the pooled overall finding for all populations combined.
Benefits of increased milk intake might be particularly noticeable in
East Asian countries where strokes are relatively more common, and milk
consumption is much lower than those studies conducted among European or
American populations \citep{dehghan2018association}. However, the Life
Span Study \citep{sauvaget2003intake}, which was conducted about 10
years earlier than the JACC Study, reported null association between
milk intake and fatal stroke among men and women combined who survived
from the Hiroshima and Nagasaki atomic bomb. The difference could be
largely explained by the different targeting populations between the two
studies. \citet{kondo2013consumption} also reported null association in
either men or women from the NIPPON DATA80 study. In fact, the exact
number of stroke mortality events was about 85\% less and the number of
participants in the NIPPON DATA80 was about 90\% less than those in the
JACC study database, their null association might likely due to its
limited statistical power. \citet{umesawa2008dietary} reported that
dairy calcium intake was inversely associated with ischemic stroke
mortality risk which could be considered as one of the potential
evidence that supported our findings. Furthermore, stronger inverse
association between milk consumption and stroke mortality in men rather
than in women was found in the Singapore Chinese Health Study
\citep{Talaei_2016} as well. The reasons for this gender differences is
currently unknown. It might be contributed by generally better/healthier
lifestyles (much less smokers and alcohol drinkers) in women regardless
of milk intake frequency, or maybe due to other factors that was not
available in/considered by our models such as intake of calcium
supplements. The probably existing beneficial effect by milk intake is
probably less evident in women than that in men. Further investigation
is needed.
